---
title: "Alcohol vs Seat choice"
author: "Areli Nava"
date: "summer 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

```{r eval=FALSE}
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
library(ggplot2)

# Create the notched box plot with red outliers
ggplot(davisdata, aes(x = Seat, y = alcohol)) +
  geom_boxplot(notch = TRUE, outlier.colour = "red") +
  labs(title = "Notched Box plot by Seat") +
  theme(plot.title = element_text(hjust = 0.5))
```



  


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

the people in the back are drinking a lot more than the people in the middle and the front. The data shows that min all equals 0, but the median, the people in the back have 4 and the people in the middle have 1 while the front people have none.There is a big difference between the means, with the people in the back having the highest of almost a 10 round up while the people in the middle have 3 and the people in the front have a 2 rounded up. Most people are sitting in the middle with a number of 83, and the rest are evened out between the back and the front. You can find those numbers under the letter "n".


## Inferential Tests

## Conclusions


